\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[default]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
\usepackage{newtxtext,newtxmath}
% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    {\Huge \scshape Runqiu Ye} \\ \vspace{5pt}
    \small \raisebox{-0.1\height}\faPhone\ 412-519-5386 ~ 
    {\raisebox{-0.1\height}\faEnvelope\ 
    {runqiuy@andrew.cmu.edu}} ~ 
    {\raisebox{-0.1\height}\faLinkedin\ 
    \href{https://www.linkedin.com/in/runqiu-ye/}
    {\underline{linkedin.com/in/runqiu-ye}}}  ~
    {\raisebox{-0.1\height}\faGithub\ 
    \href{https://github.com/RunqiuYe}
    {\underline{github.com/RunqiuYe}}}
\end{center}
\vspace{-5pt}


%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart
\resumeSubheading
  {\textbf{Carnegie Mellon University}}{Expected Graduation 2027}
  {Computer Science, Mathematics}
  {Pittsburgh, Pennsylvania}
\resumeItemListStart
\resumeItem{\textbf{GPA:} 3.97 / 4}
\resumeItem{\textbf{Computer Science Coursework:} 
Machine Learning (PhD), 
Natural Language Processing (PhD), 
Probabilistic Graphical Models (PhD), 
Computer Systems, 
Parallel and Sequential Data Structures and Algorithms,
Functional Programming, 
Theoretical Computer Science.}
\resumeItem{\textbf{Mathematics Coursework:} 
Probability Theory, 
Honor Linear Algebra, 
Matrix and Vector Calculus, 
Honor Real Analysis, 
Honor Abstract Algebra, 
Functional Analysis, 
Measure Theory, 
Differential Geometry.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-10pt}

%-----------PROGRAMMING SKILLS-----------
\section{SKILLS AND AWARDS}
\begin{itemize}[leftmargin=0in, label={}]
  \small{\item{
   \textbf{Language/Libraries:} 
   C, 
   C++, 
   Python, 
   Java, 
   Fortran, 
   PyTorch, 
   TensorFlow, 
   Mujoco, 
   Numpy, 
   Pandas, 
   Matplotlib. \\
   \textbf{Developer Tools:} 
   VS Code, 
   Git, 
   Github, 
   Colab, 
   Anaconda, 
   Jupyter Lab. \\
   \textbf{Awards:} 
   CMU Summer Undergraduate Research Fellowship, 
   Dean List High Honors, 
   Chinese Mathematics Olympiads First Prize,
   Chinese Physics Olympiads First Prize,
   International Young Physicists' Tournament Champion, 
   Princeton University Physics Competition 2nd Place, 
   Twice top 5\% in AMC 12 and AIME qualifier.
  }}
\end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  
\resumeSubHeadingListStart
\resumeSubheading
{\textbf{Amazon Web Services (AWS)}}
{May 2025 -- August 2025}
{Incoming Software Developer Intern}
{Seattle, Washington}
\resumeItemListStart
\resumeItem{Incoming \textbf{software developer intern} at 
Amazon.}
\resumeItemListEnd

\resumeSubheading
{\textbf{Carnegie Mellon University} 
$ \; | \; $ 
{Deep Reinforcement learning, Imitation Learning}}
{September 2024 -- January 2025}
{Undergraduate Research Intern in Robotics}
{Pittsburgh, Pennsylvania}
\resumeItemListStart
\resumeItem{Used \textbf{imitation learning} and 
\textbf{reinforcement learning} in loco-mujoco to build 
\textbf{individual-specific physics simulation} for joint 
torque \textbf{from vision data}. Investigate
the interactions of \textbf{foot models} and 
\textbf{ground reaction force} to better simulate 
human muscles and joints.}
\resumeItem{Researched \textbf{computer vision-based 
wearable robotic exoskeleton} for improving human mobility. 
Utilized integrated data from \textbf{motion capture}, 
\textbf{vision}, and \textbf{sensors} to estimate 
\textbf{whole-body movement and posture}, enhancing 
efficacy of exoskeleton control.
\\
Github link: \href{https://github.com/RunqiuYe/loco-mujoco/tree/metamobility-ray}
{\underline{github.com/RunqiuYe/loco-mujoco}}}
\resumeItemListEnd

\resumeSubheading
  {\textbf{Carnegie Mellon University} 
  $ \; | \; $ 
  {Python, fortran, Data analysis, github}}
  {January 2024 -- August 2024}
  {Undergraduate Research Intern in Computational 
  Astrophysics}
  {Pittsburgh, Pennsylvania}
\resumeItemListStart
\resumeItem{Utilized \textbf{Python and Fortran} to 
develop a \textbf{high-precision numerical simulation} 
for evolution of binary star systems, resulting in 
simulation of over \textbf{1.5 million binary stars} 
in Pittsburgh Supercomputing Center and 
\textbf{deepened insights of white dwarf formation.}}

\resumeItem{Implemented \textbf{statistical analysis} 
with Python to simulation results to study dependency between 
certain evolution models and binary stars behaviors, 
resulting in \textbf{creation of new models} and 
\textbf{70\% more consistent results} between different 
simulations.}

\resumeItem{Received \textbf{2024 Summer Undergraduate 
Research Fellowship Awards}.
Github link: 
\href{https://github.com/RunqiuYe/post-MT-binaries}
{\underline{github.com/RunqiuYe/post-MT-binaries}}.}
\resumeItemListEnd
    
\resumeSubHeadingListEnd

\vspace{-10pt}

%-----------PROJECTS-----------
\section{PROJECTS}
\vspace{-5pt}
  \resumeSubHeadingListStart

  \resumeProjectHeading
  {\textbf{Attention and Transformer} 
  $ \; | \; $ 
  {PyTorch, Deep learning, Natural language processing}}
  {Spring 2025}
  \resumeItemListStart
  \resumeItem{
  Implemented a \textbf{transformer encoder and decoder}
  from scratch. \textbf{Improved by 
  using SwiGLU and different normalization}.
  }
  \resumeItem{
  Trained and tested on \textbf{sentiment analysis task using 
  Yelp dataset}. Achieved \textbf{top-in-class 86\% accuracy}
  on heldout test dataset.
  }
  \resumeItemListEnd

  \vspace{-13pt}

  \resumeProjectHeading
  {\textbf{Computer System Projects} 
  $ \; | \; $ 
  Computer systems, C programming, 
  Parallel programming}
  {Fall 2024}
  \resumeItemListStart
  \resumeItem{
  Created a \textbf{dynamic memory allocator} (malloc lab), 
  a \textbf{Linux shell} (shell lab), a \textbf{multithreaded
  proxy server} (proxy lab), and a \textbf{parallel file system} 
  (sfs lab) using \textbf{system level C}, deepening
  \textbf{understanding of computer system and parallel programming}.}
  \resumeItemListEnd

  \vspace{-13pt}  

  \resumeProjectHeading
  {\textbf{Handwritten Digits Classifier} 
  $ \; | \; $ 
  {Deep learning, Convolutional neural network}}
  {August 2024}
  \resumeItemListStart
  \resumeItem{
  Built a \textbf{convolutional neural network} 
  to classify grayscale handwritten digits. \textbf{Trained
  with 60000 images} from the MNIST dataset.}
  \resumeItem{
  Tested on 400 examples and \textbf{achieved 
  80\% accuracy}. Planned extension into
  \textbf{LaTeX symbol and equation translator}.}
  \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-15pt}


\end{document}
